COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2020-07-07 main.tex
Add acknowledgements section

>>>>

\section*{Acknowledgements}
This work was facilitated through the use of advanced computational, storage and networking infrastructure provided by the Hyak supercomputer system at the 
University of Washington. We acknowledge the people of the Dkhw’Duw’Absh, the Duwamish Tribe, the Muckleshoot Tribe, and other tribes on whose traditional 
lands we have performed this work.

\textit{Software:} Astropy \citep{2013A&A...558A..33A}, {\sc CASA} \citep{2007ASPC..376..127M}, {\sc ChaNGa} \citep{2008IEEEpds...ChaNGa, 2015AphCom..2..1}, Matplotlib \citep{2007CSE.....9...90H}, NumPy \citep{2011CSE....13b..22V}, Pandas \citep{mckinney-proc-scipy-2010}, {\sc PYNBODY} \citep{2013ascl.soft05002P}, {\sc sklearn} \citep{scikit-learn},
